---
title: "EDA Usage of Analysis"
author: "Alain Lesaffre"
date: "23 October 2015"
output: html_document
---
```{r, echo=FALSE, message=FALSE}
Curtin  <- FALSE
library(dplyr)
library(knitr)
library(ggplot2)
if( Curtin == TRUE){
        source( "/Users/Alain/Dropbox/HealthHack/Health-Hack/code/common.R")
}else{
        source( "/Users/Alain/Documents/My Data Analysis/Health-Hack/code/common.R")   
}
```

###Summary

First analysis of the data about usage and quality of analysis in one Perth Hospital. The data are from the Perth Health Hack hold on the 23rd October 2015.

###What do we have? 
```{r, echo=FALSE}
if(file.exists(preprocessdataset)){
  dataset <-readRDS(preprocessdataset)       
}else{
  dataset <-read.csv(orgdata, sep="\t", colClasses = typeread)
}  

numberpatients <-length(unique(dataset$Patient_ID))
numbprocedures <-length(unique(dataset$Request_ID))
```
The data are made of 18 variables for ```r numberpatients``` patients  and ```r numbprocedures``` number of procedures. The variables are:

1. Patient_ID: A reference id such as ```r dataset$Patient_ID[1]```, current range ```r range(dataset$Patient_ID)```

2. Index_ID:   Identifier for one set of analysis, there are ```r length(unique(dataset$Request_ID))``` in the current dataset. 

3. data_coln:  The date the current analysis has been collected, the format seems to base on a starting date. __The 1 January 1970 is not the strating date, to be checked__

4. cc_order: It is the reference number of the ward, the ward field is not unique, for report by ward we should use the cc_number

####Exploration first patient
```{r, echo=FALSE}
firstpatient <-dataset %>% filter(Patient_ID == Patient_ID[1] &  Request_ID ==  Request_ID[1])
patientprocedures <- firstpatient  %>% select(11:18)  #We cut


```

The first patient is from the ward ```r firstpatient$ward[1]```, what is surprizing is that all the ```r dim(firstpatient)[1]``` have been collected on the same day. __We have to check if this is one error__. 
Out of the ```r dim(firstpatient)[1]``` procedures, ```r sum(patientprocedures$alpha =="/")``` are negative as signaled by the / character. What should be check is why do we have empty alpha in our case we have ```r   sum(patientprocedures$alpha == "")```, _to be checked_.

The type of panel name is always similar and is ```r firstpatient$panelname[1]```. 


In this case the antibiotic name could be surprising for example ```r firstpatient$antibiotic.name[37]``, which doe not seem as antibitic but have one other meaning to _verify_. 

#### All patients
```{r, echo=FALSE}
numberallnegative = sum(dataset$alpha == "/")
```

As the number of negatives is important, we can do a quick check using the alpha / negative result.  We have ```r numberallnegative ``` or ```r numberallnegative / nrow(dataset)``` % of negative. Which is really the case very high. 






####Transformation 
It appears that we can build two tables:

1. One of patient itemt reference 

2. One for the analysis 

